Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-10 paper.qmd
Need to update Figure 11

trimesh_removed_gau1 <- vis_rmlg_mesh(
  distance_edges = distance_gau1,
  benchmark_value = benchmark_gau1,
  tr_coord_df = tr_from_to_df_gau1,
  distance_col = "distance")

@@

@@

trimesh_removed_gau1 <- vis_rmlg_mesh(
  distance_edges = distance_gau1,
  benchmark_value = benchmark_gau1,
  tr_coord_df = tr_from_to_df_gau1,
  distance_col = "distance")

@@

tsne_gau + umap_gau + pacmap_gau +
five_gau_proj_tsne_model1 + five_gau_proj_umap_model1 + five_gau_proj_pacmap_model1 + five_gau_proj_tsne_model2 + five_gau_proj_umap_model2 + five_gau_proj_pacmap_model2 +
  plot_layout(guides = "collect", nrow = 3) &
  theme(legend.position='none')
```

>>>>

# trimesh_removed_gau1 <- vis_rmlg_mesh(
#   distance_edges = distance_gau1,
#   benchmark_value = benchmark_gau1,
#   tr_coord_df = tr_from_to_df_gau1,
#   distance_col = "distance")

tr_df <- distinct(tibble(
  x = c(tr_from_to_df_gau1[["x_from"]], tr_from_to_df_gau1[["x_to"]]), 
  y = c(tr_from_to_df_gau1[["y_from"]], tr_from_to_df_gau1[["y_to"]])))

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1)

tr_from_to_df_gau1 <- inner_join(
  tr_from_to_df_gau1, distance_df_small_edges_gau1, 
  by = c("from", "to"))

trimesh_removed_gau_tsne <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = tsne_gau_scaled,
    aes(
      x = tSNE1,
      y = tSNE2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  coord_fixed() +
  interior_annotation("a1", 
                      position = c(0.08, 0.95),
                      cex = 2)

@@

tr_df <- distinct(tibble(
  x = c(tr_from_to_df_gau1[["x_from"]], tr_from_to_df_gau1[["x_to"]]), 
  y = c(tr_from_to_df_gau1[["y_from"]], tr_from_to_df_gau1[["y_to"]])))

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1)

tr_from_to_df_gau1 <- inner_join(
  tr_from_to_df_gau1, distance_df_small_edges_gau1, 
  by = c("from", "to"))

trimesh_removed_gau_umap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = umap_gau_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  coord_fixed() +
  interior_annotation("b1", 
                      position = c(0.06, 0.95),
                      cex = 2)

@@

# trimesh_removed_gau1 <- vis_rmlg_mesh(
#   distance_edges = distance_gau1,
#   benchmark_value = benchmark_gau1,
#   tr_coord_df = tr_from_to_df_gau1,
#   distance_col = "distance")

tr_df <- distinct(tibble(
  x = c(tr_from_to_df_gau1[["x_from"]], tr_from_to_df_gau1[["x_to"]]), 
  y = c(tr_from_to_df_gau1[["y_from"]], tr_from_to_df_gau1[["y_to"]])))

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1)

tr_from_to_df_gau1 <- inner_join(
  tr_from_to_df_gau1, distance_df_small_edges_gau1, 
  by = c("from", "to"))

trimesh_removed_gau_pacmap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = pacmap_gau_scaled,
    aes(
      x = PaCMAP1,
      y = PaCMAP2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  coord_fixed() +
  interior_annotation("c1", 
                      position = c(0.08, 0.95),
                      cex = 2)

@@

trimesh_removed_gau_tsne + trimesh_removed_gau_umap + trimesh_removed_gau_pacmap +
five_gau_proj_tsne_model1 + five_gau_proj_umap_model1 + five_gau_proj_pacmap_model1 + five_gau_proj_tsne_model2 + five_gau_proj_umap_model2 + five_gau_proj_pacmap_model2 +
  plot_layout(guides = "collect", nrow = 3) &
  theme(legend.position='none')
```
